Software architectures to integrate workflow engines in science gateways

### 2016-05-15 paper.tex
Fixed #25

\begin{figure*}
\centering
\hspace*{0.2\columnwidth}
\subfloat[Tight integration]{
\def\svgwidth{0.6\columnwidth}
\input{figures/tight.pdf_tex}
\label{archi:tight}
}
\hfill
\subfloat[Service invocation]{
\def\svgwidth{0.6\columnwidth}
\input{figures/service.pdf_tex}
\label{archi:service}
\hspace*{0.2\columnwidth}
}\\
\hspace*{0.2\columnwidth}
\subfloat[Task encapsulation]{
\def\svgwidth{0.6\columnwidth}
\input{figures/sub-task.pdf_tex}
\label{archi:sub-task}
}
\hfill
\subfloat[Pool]{
\def\svgwidth{0.6\columnwidth}
\input{figures/agent.pdf_tex}
\label{archi:agent}
\hspace*{0.2\columnwidth}
}\\
\subfloat[Nested workflows. Left: abstract model. Right: instantiation with service invocation.]{
\def\svgwidth{0.9\columnwidth}
\input{figures/nested-1.pdf_tex}
\def\svgwidth{0.9\columnwidth}
\input{figures/nested-2.pdf_tex}
\label{archi:nested}
}\\
\subfloat[Workflow conversion. Left: abstract model. Right: instantiation with service invocation.]{
\def\svgwidth{0.5\columnwidth}
\input{figures/import-1.pdf_tex}
\hfill
\def\svgwidth{0.5\columnwidth}
\input{figures/import-2.pdf_tex}
\label{archi:import}
}
\caption{Architectures}
\label{fig:architectures}
\end{figure*}
\begin{table*}
\centering
\footnotesize
\rowcolors{1}{white}{gray!25}
\begin{tabular}{ll}
  \textbf{Architecture} & \textbf{Systems} \\
  \hline
  Tight & \pbox{1.5\columnwidth}{
          Catania Science Gateway Framework~\cite{ardizzone2012decide},
          Distributed application runtime environment (DARE~\cite{maddineni2012distributed}),
          DECIDE~\cite{ardizzone2012decide}$^{c,n}$, LONI Pipeline Environment$^n$~\cite{dinov2009efficient}
          }
  \\
  Service & \pbox{1.5\columnwidth}{
            Apache Airvata~\cite{marru2011apache}, Neuroscience Gateway~\cite{shahand2015data}$^{w,n}$, HubZero with Pegasus~\cite{CPE:CPE3257}, MoSGrid~\cite{kruger2014mosgrid}$^w$, System in~\cite{wu2010accelerating}, Vine Toolkit~\cite{DBLP:journals/scpe/SzejnfeldDKKKKLPTWDNW10}, Virtual Imaging Platform~\cite{GLAT-13}$^n$, WS-PGRADE/gUSE framework~\cite{Kacsuk2012},
            Science gateways in~\cite{kacsuk2014science}$^w$
            } \\
  Task & CBRAIN and PSOM~\cite{GLAT-16}$^n$, CBRAIN and FSL$^n$\\
  Pool & SHIWA pool~\cite{ROGE-13}\\
  Nested & \pbox{1.5\columnwidth}{SHIWA Simulation Platform (Coarse-Grained Interoperability~\cite{terstyanszky2014enabling})$^w$, HubZero with Pegasus (via hierarchical workflows)~\cite{Deelman201517}, Tavaxy~\cite{Abouelhoda2012}.
           }\\
  Conversion & SHIWA Simulation Platform (Fine-Grained Interoperability)~\cite{plankensteiner-prodan-etal:2013}$^w$, Tavaxy~\cite{Abouelhoda2012}, system in~\cite{delaGarza2016}.
\end{tabular}
\caption{Classification of science gateways based on the architecture used to integrate workflow engines. $^c$: based on the Catania Science Gateway Framework. $^w$: based on WS-PGRADE/gUSE. $^n$: used for neuroimaging.}
\label{table:system-classification}
\end{table*}

@@

This architecture is largely adopted in systems such as Apache
Airvata~\cite{marru2011apache}, Vine
Toolkit~\cite{DBLP:journals/scpe/SzejnfeldDKKKKLPTWDNW10}, Virtual
Imaging Platform~\cite{GLAT-13}, the systems
in~\cite{wu2010accelerating,shahand:2012jgc} and the WS-PGRADE/gUSE
framework~\cite{Kacsuk2012}. The integration between the
HubZero science gateway and the Pegasus workflow engine performed
in~\cite{CPE:CPE3257} also uses a service architecture, where the
\texttt{d} interaction is implemented as a set of calls to Pegasus'
command-line tools (e.g., pegasus-status, pegasus-plan,
etc.). Figure~\ref{fig:vip-architecture} shows the architecture of the
Virtual Imaging Platform, where the MOTEUR workflow
engine~\cite{GLAT-08i} is invoked through a service.

>>>>

\begin{figure*}
\centering
\hspace*{0.2\columnwidth}
\subfloat[Tight integration]{
\def\svgwidth{0.6\columnwidth}
\input{figures/tight.pdf_tex}
\label{archi:tight}
}
\hfill
\subfloat[Service invocation]{
\def\svgwidth{0.6\columnwidth}
\input{figures/service.pdf_tex}
\label{archi:service}
\hspace*{0.2\columnwidth}
}\\
\hspace*{0.2\columnwidth}
\subfloat[Task encapsulation]{
\def\svgwidth{0.6\columnwidth}
\input{figures/sub-task.pdf_tex}
\label{archi:sub-task}
}
\hfill
\subfloat[Pool]{
\def\svgwidth{0.6\columnwidth}
\input{figures/agent.pdf_tex}
\label{archi:agent}
\hspace*{0.2\columnwidth}
}\\
\subfloat[Nested workflows. Left: abstract model. Right: instantiation with service invocation.]{
\def\svgwidth{0.9\columnwidth}
\input{figures/nested-1.pdf_tex}
\def\svgwidth{0.9\columnwidth}
\input{figures/nested-2.pdf_tex}
\label{archi:nested}
}\\
\subfloat[Workflow conversion. Left: abstract model. Right: instantiation with service invocation.]{
\def\svgwidth{0.5\columnwidth}
\input{figures/import-1.pdf_tex}
\hfill
\def\svgwidth{0.5\columnwidth}
\input{figures/import-2.pdf_tex}
\label{archi:import}
}
\caption{Architectures}
\label{fig:architectures}
\end{figure*}
\begin{table*}
\centering
\footnotesize
\rowcolors{1}{white}{gray!25}
\begin{tabular}{ll}
  \textbf{Architecture} & \textbf{Systems} \\
  \hline
  Tight & \pbox{1.5\columnwidth}{
          Catania Science Gateway Framework~\cite{ardizzone2012decide},
          Distributed application runtime environment (DARE~\cite{maddineni2012distributed}),
          DECIDE~\cite{ardizzone2012decide}$^{c,n}$, LONI Pipeline Environment$^n$~\cite{dinov2009efficient}
          }
  \\
  Service & \pbox{1.5\columnwidth}{
            Apache Airvata~\cite{marru2011apache}, Neuroscience Gateway~\cite{shahand2015data}$^{w,n}$, HubZero with Pegasus~\cite{CPE:CPE3257}, MoSGrid~\cite{kruger2014mosgrid}$^w$, System in~\cite{wu2010accelerating}, Vine Toolkit~\cite{DBLP:journals/scpe/SzejnfeldDKKKKLPTWDNW10}, Virtual Imaging Platform~\cite{GLAT-13}$^n$, WS-PGRADE/gUSE framework~\cite{Kacsuk2012},
            Science gateways in~\cite{kacsuk2014science}$^w$, GridSFEA~\cite{Elts2010}
            } \\
  Task & CBRAIN and PSOM~\cite{GLAT-16}$^n$, CBRAIN and FSL$^n$\\
  Pool & SHIWA pool~\cite{ROGE-13}\\
  Nested & \pbox{1.5\columnwidth}{SHIWA Simulation Platform (Coarse-Grained Interoperability~\cite{terstyanszky2014enabling})$^w$, HubZero with Pegasus (via hierarchical workflows)~\cite{Deelman201517}, Tavaxy~\cite{Abouelhoda2012}.
           }\\
  Conversion & SHIWA Simulation Platform (Fine-Grained Interoperability)~\cite{plankensteiner-prodan-etal:2013}$^w$, Tavaxy~\cite{Abouelhoda2012}, system in~\cite{delaGarza2016}.
\end{tabular}
\caption{Classification of science gateways based on the architecture used to integrate workflow engines. $^c$: based on the Catania Science Gateway Framework. $^w$: based on WS-PGRADE/gUSE. $^n$: used for neuroimaging.}
\label{table:system-classification}
\end{table*}

@@

This architecture is largely adopted in systems such as Apache
Airvata~\cite{marru2011apache}, Vine
Toolkit~\cite{DBLP:journals/scpe/SzejnfeldDKKKKLPTWDNW10}, Virtual
Imaging Platform~\cite{GLAT-13}, the systems
in~\cite{wu2010accelerating,shahand:2012jgc} and the WS-PGRADE/gUSE
framework~\cite{Kacsuk2012}. The integration between the
HubZero science gateway and the Pegasus workflow engine performed
in~\cite{CPE:CPE3257} also uses a service architecture, where the
\texttt{d} interaction is implemented as a set of calls to Pegasus'
command-line tools (e.g., pegasus-status, pegasus-plan,
etc.). Figure~\ref{fig:vip-architecture} shows the architecture of the
Virtual Imaging Platform, where the MOTEUR workflow
engine~\cite{GLAT-08i} is invoked through a service. GridSFEA~\cite{Elts2010} 
uses WS-VLAM as a WS-RF service.
